Quantum Hoare Type Theory

### 2020-05-05 ms-paper/ms-paper.tex
Another missing todo
Update ms-paper.tex

\subsubsection{Judgments}
The type system is designed to be bidirectional and syntax directed and hences include separate judgements for intro and elim terms. We are able to use them unchanged for QHTT.

@@

\section{Teleportation}
\label{app:teleport}
% \todo{TODO: Refine assertions}
\subsection{Alice's circuit}
\begin{lstlisting}[language=QHaskell]
alice : \Pi a : Qbit. \Pi e : Qbit
        {(Id(a, -) /\ entangled(e)}
           r : (Bool, Bool)
        {emp}
      = \a.\e.do applyU (ifQ a (X e));
                 applyU (H a);
                 (measQbit a, measQbit e)
\end{lstlisting}

>>>>

\subsubsection{Judgments}
The type system is designed to be bidirectional and syntax directed and hence includes separate judgements for intro and elim terms. We are able to use them unchanged for QHTT.

@@

\section{Teleportation}
\label{app:teleport}
\todo{TODO: Refine assertions}
\subsection{Alice's circuit}
\begin{lstlisting}[language=QHaskell]
alice : \Pi a : Qbit. \Pi e : Qbit
        {(Id(a, -) /\ entangled(e)}
           r : (Bool, Bool)
        {emp}
      = \a.\e.do applyU (ifQ a (X e));
                 applyU (H a);
                 (measQbit a, measQbit e)
\end{lstlisting}
